DRAFT \\ From physical principles to classical and quantum \\ Hamiltonian and Lagrangian particle mechanics

### 2016-10-03 2015CompleteDerivation/completeDerivation.tex
Adding figure for discontinuous maps

>>>>

\begin{figure}
	\includestandalone[width=\columnwidth]{pictures/continuousMap}
	\caption{A continuous function always maps finite precision knowledge in the vertical axis (i.e. an open set) to finite precision knowledge in the horizontal axis. A discontinuous function may map to finite precision (i.e. a closed set). If finite precision identification is ruled out (i.e. use of standard topology) then discontinuous functions must also be ruled out.}
	\label{fig:continuous_map}
\end{figure}
